### 2013-04-01 exam6/2.tex
BST iterator extra credit.
abandon the outline problem

\noindent
\item Write a note visitor that produces the numbered outline of a
  note.  The result should be an \texttt{ArrayList} of
  \texttt{String}s.  For example, the numbered outline of the note
  note is an \texttt{ArrayList<String>} with the following elements:

\begin{verbatim}
"1. NSF Proposal 1218390"
"1.1. Overview"
"1.1.1. WAT?"
"1.1.2. Motivations"
"1.1.2.1. unmotivating"
"1.2. Middle (fell asleep)"
"1.3. Conclusions"
"1.4. Budget"
"1.4.1. very large"
"1.4.2. lots of BU undergrads"
\end{verbatim}

@@

>>>>

\noindent
\item Write a note visitor that produces the maximum nesting depth of
  a note.  For example, the maximum nesting depth of the given example
  is 4.

%  numbered outline of a
%   note.  The result should be an \texttt{ArrayList} of
%   \texttt{String}s.  For example, the numbered outline of the note
%   note is an \texttt{ArrayList<String>} with the following elements:

% \begin{verbatim}
% "1. NSF Proposal 1218390"
% "1.1. Overview"
% "1.1.1. WAT?"
% "1.1.2. Motivations"
% "1.1.2.1. unmotivating"
% "1.2. Middle (fell asleep)"
% "1.3. Conclusions"
% "1.4. Budget"
% "1.4.1. very large"
% "1.4.2. lots of BU undergrads"
% \end{verbatim}

@@

\begin{problem}  \pts{5}

{\bf Extra Credit}

\noindent
Revise your design of \texttt{BST<X>} to implement
 \texttt{Iterable<X>} interface.  The iterator returned by
 \texttt{iterator()} should iterate through the elements in sorted order.
